\section{Reflections on our process}
In \autoref{sec:our-process} we described the our process and the things that we used from scrum.
In this section we reflect on our process, the changes that we had done throughout the semester as well as what we would change for our future projects.

\subsubsection{Scrum}
Our scrum inspired process worked well with sprints, sprint planning, sprint backlog, product owner, product backlog and product increment.
We took turns on having the role as PO.
The PO had the task of planning the next product backlog and add a DoD onto every task in the product backlog.
This gave everyone an sense of ownership and a possibility to influence which direction should be taken for the given week.
\\\\
When we conducted the sprint planning, we would discuss the every element in the product backlog and estimate how many story points each task should have.
This gave everyone the same understanding on how the given tasks should be solved and eliminate most ambiguities. 
\\\\
However, later in the project when we started to develop the application and learning \textit{React}, it started to become less systematic.
This was often due to it being difficult to estimate how long each task would take to solve.
\\\\
We also stopped conducting the retrospective meetings. 
This could have helped making the project more structured as we could have discussed the problems that we faced and the reasons why we did not complete our tasks in time.

\subsubsection{Formal reviews}
The formal reviews was something that we changed in the middle of the semester, so that two people had to review a pull request together and not individually.
Formal reviews were described in \autoref{sec:formal-reviews}.
The first hour of every workday was spent on reviewing pull requests.
\\\\
This increased the quality of the pull requests, as more errors were caught when two people had to debate the code.
This is however more time consuming and more difficult to plan.
If two people are in process of reviewing a pull request another person can be waiting for them to finish if they are assigned a pull request with one of them. 
Then when a pull request have been reviewed and if changes are requested, then these people have to come back to review the changes.

\subsubsection{Working from home}

\subsubsection{Supervisor meetings}


